Response to the defense feedback

### 2021-06-22 Chapter-7/Chapter-7.tex
Updates from Overleaf

In Chapter~\ref{chapter5}, we propose a fuzzing method to automatically detect and quantify the address-based side-channel leakages automatically. The proposed method can produce an estimation of the side-channel leakage of the deterministic program. As a result, any severe leakage reported by \ctool{} is a true severe leakage. We also study the total effect of two leakages. Using statistical hypothesis testing, we are able to determine if the two leakages are independent. If so, we can calculate the sum of the amount of leakage by adding them. Our evaluation result on both several libraries and benchmarks show that \ctool{} is effective and accurate in detecting the side-channel leakage.

In conclusion, this dissertation research develops practical techniques for precise side-channel analysis in software systems. For each proposed method, we implement and evaluate it on real-world software. The evaluation results show the effeteness and generality of our proposed method.  We also release the prototypes to facilitate future research in the area.
\section{Future Directions}
There are a few potential directions to extend the dissertation research.

>>>>

In Chapter~\ref{chapter5}, we propose a fuzzing method to detect and quantify the address-based side-channel leakages automatically. The proposed method can produce an estimation of the severity level of each side-channel leakage of a deterministic program. As a result, any severe leakage reported by \ctool{} is a true severe leakage. We also study the total effect of two leakages. Using statistical hypothesis testing, we are able to determine if any two different leakages are independent. If so, we can calculate the sum of the amount of leakage by adding them. Our evaluation result on several libraries and benchmarks show that \ctool{} is effective and accurate in detecting the side-channel leakage.

In conclusion, this dissertation research develops practical techniques for precise side-channel analysis in software systems. For each proposed method, we implement and evaluate it on real-world software. The evaluation results show the effectiveness and generality of our proposed method.  We also release the prototypes to facilitate future research in the area.
\section{Future Directions}
There are a few potential directions to extend the dissertation research.
